Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

\section{Computational details}
All the calcualtions presented in this paper are performed with the BigDFT code,
which uses Daub

>>>>

\section{Computational details}
The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{bigdft},
which employs Daubechies Wavelets as computational basis set.
Such basis present optimal features of in view of reproducibility of the results,
ans it has proven to represent precisely and explicitly system with Free boundary conditions, without any basis set superposition error nor supercell aliasing.
For Ground State results, the important parameters in the context of convergence of the calculations are the spacing of the wavelet grid and the size of the simulation domain: for bound-state like functions, convergence is achieved by reducing the grid spacing and increasing the simulation box size.
Norm Conserving Pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proven to be able to provide all-electron accuracy for molecular systems.

Our LR calculation are performed with the Casida formalism \cite{bhaarathi}, where
